### 2024-07-04 latex-article/article.tex
Automate thumbnails for readme (h/t @andrewheiss)

\documentclass[12pt]{article}
\usepackage{paper}
\usepackage{math}
\addbibresource{references.bib}

\title{Example Paper\thanks{\acknlowledgements}}
\author{
  Author One%
  \thanks{School. Email: \href{mailto:email@gmail.com}{email@gmail.com}.} 
  \ and 
  Author Two%
  \thanks{School. Email: \href{mailto:email@gmail.com}{email@gmail.com}.}
}
\date{\textsc{\today}}
\def\acknlowledgements{%
  Acknlowedgements
}

@@

  \par~\par\noindent
  {\color{asher}JEL-Classification:} ...
  \par\noindent
  {\color{asher}Keywords:} ...
  \par\vspace{-2.5mm}
\end{abstract}

\newpage

@@

Hi and welcome to my default paper template. I tried to make the theme minimal and beautiful while able to do all the things that I want it to do. These include making it easy to make figures/tables with notes; have powerful math commands; have nice readable typography; make co-authoring in a document easy; have a nice looking bibliography; and make appendices easy. \kyle{I'm including this comment for coauthors. If I switch above to \texttt{togglefalse}, this will dissapear.} I'll show off these things, but make sure to check the source code alongside to see how simple it is to typset with this.

See below for \autoref{thm:residue_thm}, the regression specification (\autoref{eq:fe_reg}), \autoref{tab:summ_stat}, \autoref{fig:event_timing}, appendix \autoref{tab:reg1}. Of course, make sure to touch up on your micro theory with \citet{mas1995microeconomic}. I also provide a set of colors: \navy{Navy}, \teal{Teal}, \purple{Purple}, \cranberry{Cranberry}, \orange{Orange}.

@@

\texttt{\textbackslash P}, \texttt{\textbackslash prob}, \texttt{\textbackslash cov}, and \texttt{\textbackslash var} work the same way too:
$$\P \quad \P[i] \quad \P{X_i} \quad \P[i]{D_i} \quad \P{\bar{X}_n > \bar{X}}{\mu = \mu_0} \quad \P[\mu]{X}{D = 1}$$
$$\cov{X_n, Y_n} \quad \var[i](\bar{X}_n)$$

@@

% ------------------------------------------------------------------------------
\newpage
% \bibliography{references.bib}
\printbibliography
% ------------------------------------------------------------------------------

% ------------------------------------------------------------------------------
\newpage
\appendix
% ------------------------------------------------------------------------------

@@

@@

In this table example, the table is narrower than textwidth, so I adjust the \texttt{\textbackslash note} width.

>>>>

\documentclass[12pt]{article}
\usepackage{paper,math}
\addbibresource{references.bib}

\title{Example Paper Title\thanks{\acknlowledgements}}
\author{
  Author One\\ {\itshape\large Affiliation}
  \and 
  Author Two\\ {\itshape\large Affiliation}
}
\date{\today}
\def\acknlowledgements{%
  One: \href{mailto:email@gmail.com}{email@gmail.com}. 
  Two: \href{mailto:email@gmail.com}{email@gmail.com}. 
  Acknlowedgements start here
}
\hypersetup{
  pdftitle = {Example Paper Title},
  pdfauthor = {Author One, Author Two},
}

@@

  \par~\par\noindent
  {\color{zinc700}Keywords:} ...
  \par\noindent
  {\color{zinc700}JEL-Classification:} ...
  \par\vspace{-2.5mm}
\end{abstract}
\newpage

@@

Hi and welcome to my default paper template. I tried to make the theme minimal and beautiful while able to do all the things that I want it to do. These include making it easy to make figures/tables with notes; have powerful math commands; have nice readable typography; make co-authoring in a document easy; have a nice looking bibliography; and make appendices easy. 
I'll show off these things, but make sure to check the source code alongside to see how simple it is to typset with this. 
\kyle{I'm including this comment for coauthors. If I switch above to \texttt{togglefalse}, this will dissapear.}

See below for \autoref{thm:residue_thm}, the regression specification (\ref{eq:fe_reg}), \autoref{tab:summ_stat}, \autoref{fig:event_timing}, appendix \autoref{tab:reg1}. Of course, make sure to touch up on your micro theory with \citet{mas1995microeconomic}. I also provide a set of colors: \navy{Navy}, \teal{Teal}, \purple{Purple}, \cranberry{Cranberry}, \orange{Orange}.

@@

\texttt{\textbackslash P}, \texttt{\textbackslash prob}, \texttt{\textbackslash cov}, and \texttt{\textbackslash var} work the same way too:
$$\P \quad \P[i] \quad \P{X_i} \quad \P[i]{D_i} \quad \P{\bar{X}_n > \bar{X}}{\mu = \mu_0} \quad \P[\mu]{X}{D = 1}$$
$$\cov{X_n, Y_n} \quad \var[i](\bar{X}_n) \quad \diag{x_i}$$

@@

% ------------------------------------------------------------------------------
\newpage
\printbibliography
% \bibliography{references.bib} % Uncomment this if using `natbib`
% ------------------------------------------------------------------------------

% ------------------------------------------------------------------------------
\newpage~\appendix
% ------------------------------------------------------------------------------

@@

\citet{mas1995microeconomic}

@@

The main regression equation is 
\begin{equation}
  y_i = \bm{X}_i \beta + u_i.
\end{equation}

Results are presented in \autoref{tab:reg1}. In this table example, the table is narrower than textwidth, so I adjust the \texttt{\textbackslash note} width.

### 2024-07-04 latex-slides/slides.tex
Small changes
Small update to table of contents
Automate thumbnails for readme (h/t @andrewheiss)

\documentclass[aspectratio=169,t,11pt,table]{beamer}
\usepackage{slides,math}
% \geometry{paperwidth=168mm,paperheight=94.5mm}

% Define `accent`/`accent2` colors for theme customization
% I recommend changing the top slider on this: 
% https://hslpicker.com/#1e9400
\definecolor{accent}{HTML}{006896}
\definecolor{accent2}{HTML}{940034}

\title{What is the Effect of X on Y?}
\date{\today}
\author{Kyle Butts}
\addbibresource{references.bib}
\begin{document}

@@

% \vspace{2.5mm}
% {\footnotesize $^*$ A bit of extra info here. Add an asterich to title or author}
\end{frame}
% ------------------------------------------------------------------------------

@@

\begin{frame}{Components}{Bullet Points \& Button}\label{main1}
  This section highlights commonly used components and their theming

@@

  \bottomleft{
    \hyperlink{appendix1}{\beamergotobutton{Appendix}}
    \beamergotobutton{Button 2} 
    \beamergotobutton{Button 3}
  }
\end{frame}

@@

\begin{frame}{Components}{Two Columns with Figure}
  \begin{columns}[T]
    \begin{column}{.54\textwidth}
      \includegraphics[width=\textwidth]{figures/plot_did2s_retail_slides.pdf}
    \end{column}
    \hfill
    \begin{column}{.46\textwidth}
      \begin{itemize}
      \item A point about the figure that is potentially important.
      \item Another point about the figure that is also potentially important.
      \end{itemize}
    \end{column}
  \end{columns}
\end{frame}

@@

  \bigskip
  \begin{table}[h]
    \centering
    \begin{tabular}{l cc}
      \toprule
      & (1) & (2) \\
      \midrule
      Treatment dummy & \cellcolor<1>{accent!15!white} 0.0694* & \cellcolor<2>{accent!15!white} 0.0713** \\
      & (0.0401) & (0.0381) \\
      \hline
      \rowcolor<3>{accent!15!white} State Fixed Effects & & $\checkmark$ \\
      Observations & 1,673 & 1,673 \\
      \bottomrule
    \end{tabular}
  \end{table}
\end{frame}

\begin{frame}{Table}
  \begin{columns}[T]
  \begin{column}{.4\textwidth}
    \begin{adjustbox}{max width = \textwidth, center}
      \begin{tabular}{@{} l *{2}{r} @{}} 
        \toprule
        & (1) & (2)\\ 
        \midrule

>>>>

\documentclass[aspectratio=169,t,11pt,table]{beamer}
\usepackage{slides,math}

% Optionally define `accent`/`accent2` colors for theme customization
% I recommend changing the top slider on this: https://hslpicker.com/#1e9400
\definecolor{accent}{HTML}{940034}
\definecolor{accent2}{HTML}{006896}

\title{What is the Effect of X on Y?}
\date{\today}
\author{Kyle Butts}
\addbibresource{references.bib}

\begin{document}

@@

% \bottomleft{\footnotesize $^*$A bit of extra info here. Add an asterich to title or author}
\end{frame}
% ------------------------------------------------------------------------------

@@

\begin{frame}{Components}\label{main1}
  This section highlights commonly used components and their theming

@@

  \bottomleft{
    \hyperlink{appendix1}{\beamergotobutton{Appendix}}
    \beamergotobutton{Button 2} 
  }
\end{frame}

@@

\begin{frame}{Components}{Two Columns with Figure}
  \begin{columns}[T]
    \begin{column}{.6\textwidth}
      \includegraphics[width=\textwidth]{figures/plot_did2s_retail_slides.pdf}
    \end{column}
    \hfill
    \begin{column}{.4\textwidth}
      \begin{itemize}
      \item A point about the figure that is potentially important.
      \item Another point about the figure that is also potentially important.
      \end{itemize}
    \end{column}
  \end{columns}
\end{frame}

@@

  \bigskip
  \begin{center}
    {\footnotesize\textsc{Outcome:} Log of Real Per Capita Income \\}

    \begin{tabular}{l cc}
      \toprule
      & (1) & (2) \\
      \midrule
      Treatment dummy & \cellcolor<1>{accent!15!white} 0.0694* & \cellcolor<2>{accent!15!white} 0.0713** \\
      & (0.0401) & (0.0381) \\
      \hline
      \rowcolor<3>{accent!15!white} State Fixed Effects & & $\checkmark$ \\
      Observations & 1,673 & 1,673 \\
      \bottomrule
    \end{tabular}
  \end{center}
\end{frame}

\begin{frame}{Table}
  \begin{columns}[T]
  \begin{column}{.4\textwidth}
    \tabletitle{Job Satisfaction Score}

    \begin{adjustbox}{max width = \textwidth, center}
      \begin{tabular}{@{} l *{2}{r} @{}} 
        \toprule
        & (1) & (2)\\ 
        \midrule

### 2024-07-04 referee-response/responses.tex
Make referee response document simpler
Automate thumbnails for readme (h/t @andrewheiss)

% (hide by switching to `\boolfalse`)
\booltrue{INCLUDETODOS}

% Reference main document ------------------------------------------------------
% Note: I compile to `auxiliary/` to avoid cluttering the main directory. You might neeed to delete `auxiliary/`
% \usepackage{xr}
% \externaldocument[main-]{auxiliary/article}

@@

\noindent Thank you for the additional suggestions. The reviewer's comment is marked with a left border. Our responses follow below each comment.

\section*{Summary of Revisions}

% ------------------------------------------------------------------------------
\NewRef{Referee 1}{R1}
% ------------------------------------------------------------------------------

@@

\begin{todos}
  Thoughts / plan of action. These can be hidden by toggling \texttt{INCLUDETODOS} to \texttt{\textbackslash boolfalse}. 
\end{todos}

\begin{response}
  Response
\end{response}

@@

\begin{todos}
  Thoughts / plan of action. 
\end{todos}

\begin{response}
  Response
\end{response}

% ------------------------------------------------------------------------------
\NewRef{Referee 2}{R2}
% ------------------------------------------------------------------------------

>>>>

% Reference main document ------------------------------------------------------
% Note: I compile to `auxiliary/` to avoid cluttering the main directory. You might neeed to delete `auxiliary/`
% Note: The numbering of the main document is colored, but not clickable which is kind of confusing. Not sure if I like this approach or not
% \usepackage{xr,xr-hyper}
% \externaldocument[main-]{auxiliary/article}

@@

\noindent We would like to thank the referees for their time and detailed feedback on our paper. We have done our best to respond to each and every comment. Below, the reviewer's comment is marked with a left border. Our responses follow below each comment.

\section{Summary of Revisions}

The major changes in this draft include ....

% ------------------------------------------------------------------------------
\vspace*{\bigskipamount}\NewRef{Referee 1}{R1}
% ------------------------------------------------------------------------------

\begin{refcomment}
  Full text of the referee's comment. It will automatically create a \texttt{\textbackslash subsection} with the comment number.
\end{refcomment}

\kyle{
  Thoughts / plan of action. These can be hidden by toggling \texttt{INCLUDETODOS} to \texttt{\textbackslash boolfalse}. 
}

Response

@@

Response

% ------------------------------------------------------------------------------
\vspace*{\bigskipamount}\NewRef{Referee 2}{R2}
% ------------------------------------------------------------------------------

@@

% ------------------------------------------------------------------------------
\newpage
\section*{How to use this template}
% ------------------------------------------------------------------------------

There are two main commands provided by the document. First, for each referee, a  \texttt{\textbackslash section} is created using the \texttt{\textbackslash NewRef\{Name\}\{Abbreviation\}} command. The \texttt{Name} is what will be displayed by the section and \texttt{Abbreviation} is what will label each comment.

Within each section, each referee comment will be written using \texttt{\textbackslash begin\{refcomment\} ... \textbackslash end\{refcomment\}}. This command automatically numbers the comments and labels it using the \texttt{Abbreviation} from the \texttt{NewRef} declaration. Responses to the comment should go below the \texttt{refcomment} block.
